---
title: "bellabeat"
author: "Farzan Ahmed"
date: "2022-11-25"
output: html_document
---

# How Can a Wellness Technology Company Play It Smart?

Google Data Analytics Case Study 2. This case study focuses on **Bellabeat**, a high-tech manufacturer of health-focused products for women.

The project will follow steps provided in the course:

-   The steps are in orders as follows: Ask, Prepare, Process, Analyze, Share, & Act.

-   Each of the step's has it's own roadmap which will include:

1.  Guiding Questions.

2.  Key Tasks.

3.  Deliverables.

4.  Code, if required.

## Company Overview

Urška Sršen and Sando Mur founded Bellabeat, a high-tech company that manufactures health-focused smart products. Sršen used her background as an artist to develop beautifully designed technology that informs and inspires women around the world. Collecting data on activity, sleep, stress, and reproductive health has allowed Bellabeat to empower women with knowledge about their own health and habits. Since it was founded in 2013, Bellabeat has grown rapidly and quickly positioned itself as a tech-driven wellness company for women.

## Marketing Strategy

By 2016, Bellabeat had opened offices around the world and launched multiple products. Bellabeat products became available through a growing number of online retailers in addition to their own e-commerce channel on their website. The company has invested in traditional advertising media, such as radio, out-of-home billboards, print, and television, but focuses on digital marketing extensively. Bellabeat invests year-round in Google Search, maintaining active Facebook and Instagram pages, and consistently engages consumers on Twitter. Additionally, Bellabeat runs video ads on Youtube and display ads on the Google Display Network to support campaigns around key marketing dates.

## Goal

Sršen knows that an analysis of Bellabeat's available consumer data would reveal more opportunities for growth. She has asked the marketing analytics team to focus on a Bellabeat product and analyze smart device usage data in order to gain insight into how people are already using their smart devices. Then, using this information, she would like high-level recommendations for how these trends can inform Bellabeat marketing strategy.

## Data Analysis

## Ask

### Characters and products:

#### Characters:

-   **Urška Sršen**: Bellabeat's co-founder and Chief Creative Officer.

-   **Sando Mur**: Mathematician and Bellabeat's co-founder; key member of the Bellabeat executive team.

-   **Bellabeat marketing analytics team**: A team of data analysts responsible for collecting, analyzing, and reporting data that helps guide Bellabeat's marketing strategy. You joined this team six months ago and have been busy learning about Bellabeat''s mission and business goals --- as well as how you, as a junior data analyst, can help Bellabeat achieve them.

#### Products:

-   **Bellabeat app:** The Bellabeat app provides users with health data related to their activity, sleep, stress, menstrual cycle, and mindfulness habits. This data can help users better understand their current habits and make healthy decisions. The Bellabeat app connects to their line of smart wellness products.

-   **Leaf:** Bellabeat's classic wellness tracker can be worn as a bracelet, necklace, or clip. The Leaf tracker connects to the Bellabeat app to track activity, sleep, and stress.

-   **Time:** This wellness watch combines the timeless look of a classic timepiece with smart technology to track user activity, sleep, and stress. The Time watch connects to the Bellabeat app to provide you with insights into your daily wellness.

-   **Spring:** This is a water bottle that tracks daily water intake using smart technology to ensure that you are appropriately hydrated throughout the day. The Spring bottle connects to the Bellabeat app to track your hydration levels.

-   **Bellabeat membership:** Bellabeat also offers a subscription-based membership program for users. Membership gives users 24/7 access to fully personalized guidance on nutrition, activity, sleep, health and beauty, and mindfulness based on their lifestyle and goals.

### Guiding Questions:

-   **What is the problem you are trying to solve?**

Identify the trends and insights of product's usage based on consumer type to help marketing team to create an effective marketing strategy to increase business's consumer base.

-   **How can your insights drive business decisions?**

The insights and trends can help stakeholders to make big decisions and create strategy to target consumers based on the insights.

### Key Tasks:

-   **Identify the business tasks** - completed

-   **Consider key stakeholders** - completed

### Deliverable:

-   **A clear statement of business tasks**

Gather useful insights and trends about product's usage and guide marketing team to make key decisions in designing a marketing strategy.

## Prepare

### Guiding Questions:

-   **Where is your data stored?**

The data is open-source and is available for analysis for free by the company [here](https://www.kaggle.com/arashnic/fitbit).

-   **How is the data organized? Is it in long or wide format?**

The dataset contain 18 .csv files, each file contain data about different attributes such as: daily activity, daily sleep minutes, daily steps walked, daily calories burned and so on.

-   **Are there issues with bias or credibility in this data? Does your data ROCCC?**

The data is collected by the company using there own channels and resources, so there is likely no chance of data being bias and being the company's own data the credibility is very high. The data also does ROCCC it is reliable, original, comprehensive, current, and cited.

-   **How are you addressing licensing, privacy, security, and accessibility?**

The data is open-source and provided by company, the data has been made available by [Mobius](https://www.kaggle.com/arashnic).

-   **How did you verify the data's integrity?**

The data was examined and is consistent in all attributes and data types are consistent throughout.

-   **How does it help you answer your question?**

The data will help in identifying and analyzing product usage by consumers and gaining more customers.

### Key Tasks:

-   **Download data and store it appropriately** - completed

-   **Identify how it's organized** - completed

-   **Sort and filter the data** - completed

-   **Determine the credibility of the data** - completed

### Deliverable:

-   **A description of all the data sources use**

The dataset contain 18 .csv files, and has been made available by [Mobius](https://www.kaggle.com/arashnic).

## Process

### Guiding Questions:

-   **What tools are you choosing and why?**

-   **Have you ensured your data's integrity?**

-   **What steps have you taken to ensure that your data is clean?**

-   **How can you verify that your data is clean and ready to analyze?**

-   **Have you documented your cleaning process so you can review and share those results?**

### Key Tasks:

-   **Check the data for errors** - completed

-   **Choose your tools** - completed

-   **Transform the data so you can work with it effectively** - completed

-   **Document the cleaning process** - completed

### Deliverable:

Documentation of any cleaning and manipulation of data.

#### Code:

#### Load Packages:

```{r echo=TRUE}
#install.packages("tidyverse")
#install.packages("ggpubr")
#install.packages("here")
#install.packages("skimr")
#install.packages("janitor")
#install.packages("lubridate")
#install.packages("ggrepel")

library(tidyverse)
library(ggpubr)
library(here)
library(skimr)
library(janitor)
library(lubridate)
library(ggrepel)
```

#### Import And Preview Datasets:

Now import datasets that are relevant to the analysis and questions you are trying to get answers.

```{r echo=TRUE}
#import datasets that are required for analysis
daily_activity <- read_csv("dailyActivity_merged.csv")
daily_sleep <- read_csv("sleepDay_merged.csv")
hourly_steps <- read_csv("hourlySteps_merged.csv")

#examine each of the datsets for data type and format consistency
head(daily_activity)
str(daily_activity)

head(daily_sleep)
str(daily_sleep)

head(hourly_steps)
str(hourly_steps)
```

#### Cleaning And Formatting Data

```{r echo=TRUE}
#verify number of users
n_unique(daily_activity$Id)
n_unique(daily_sleep$Id)
n_unique(hourly_steps$Id)
```

```{r echo=TRUE}
#find duplicate values and remove them
sum(duplicated(daily_activity))
sum(duplicated(daily_sleep))
sum(duplicated(hourly_steps))

daily_activity <- daily_activity %>% 
  distinct() %>% 
  drop_na()
daily_sleep <- daily_sleep %>% 
  distinct() %>% 
  drop_na()
hourly_steps <- hourly_steps %>% 
  distinct() %>% 
  drop_na()
```

```{r echo=TRUE}
#clean and rename columns
clean_names(daily_activity)
daily_activity <- rename_with(daily_activity, tolower)
clean_names(daily_sleep)
daily_sleep <- rename_with(daily_sleep, tolower)
clean_names(hourly_steps)
hourly_steps <- rename_with(hourly_steps, tolower)
```

```{r echo=TRUE}
#format date and time column
daily_activity <- daily_activity %>% 
  rename(date = activitydate) %>% 
  mutate(date = as_date(date, format = "%m/%d/%Y"))

daily_sleep <- daily_sleep %>% 
  rename(date = sleepday) %>% 
  mutate(date = as_date(date, format = "%m/%d/%Y %I:%M:%S %p" , tz = Sys.timezone()))

hourly_steps <- hourly_steps %>% 
  rename(date_time = activityhour) %>% 
  mutate(date_time = as.POSIXct(date_time, format = "%m/%d/%Y %I:%M:%S %p" , tz=Sys.timezone()))
head(hourly_steps)
```

```{r echo=TRUE}
#merge daily_activity and daily_sleep datasets
daily_activity_sleep <- merge(daily_activity, daily_sleep, by = c("id", "date"))
glimpse(daily_activity_sleep)
```

## Analyze

Now the data has been transformed and cleaned, it's time to put it to work.

### Guiding Questions:

-   **How should you organize your data to perform analysis on it?**

The data should be organized in such a way that it can be used to find the trends in smart device usage by users.

-   **Has your data been properly formatted?**

All the data has been formatted properly.

-   **What surprises did you discover in the data?**

As seen in data that there are 50% users who are using devices very actively.

-   **What trends or relationships did you find in the data?**

The trends are found in data are presented below with the following code chunks.

-   **How will these insights help answer your business questions?**

The insights will help in analyzing the smart device usage by consumers who are actively using the devices daily.

### Key Tasks:

-   **Aggregate your data so it's useful and accessible** - completed

-   **Organize and format your data** - completed

-   **Perform calculations** - completed

-   **Identify trends and relationships** - completed

### Deliverable:

#### Type Of User Per Activity Level:

```{r echo=TRUE}
#daily steps average by user
daily_average <- daily_activity_sleep %>% 
  group_by(id) %>% 
  summarise(mean_daily_steps = mean(totalsteps), mean_daily_calories = mean(calories), mean_daily_sleep = mean(totalminutesasleep))
head(daily_average)
```

Classification has been made per the following article, <https://www.10000steps.org.au/articles/counting-steps/>

```{r echo=TRUE}
#classify user type by daily average steps
user_type <- daily_average %>% 
  mutate(user_type = case_when(
    mean_daily_steps < 5000 ~ "Sedentary",
    mean_daily_steps >= 5000 & mean_daily_steps < 7499 ~ "Lightly Active",
    mean_daily_steps >= 7500 & mean_daily_steps < 9999 ~ "Moderately Active",
    mean_daily_steps >= 10000 ~ "Very Active"
  ))
head(user_type)
```

```{r echo=TRUE}
#create user type data frame with user type percentage
user_type_percent <- user_type %>% 
  group_by(user_type) %>% 
  summarise(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(user_type) %>% 
  summarise(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))

user_type_percent$user_type <- factor(user_type_percent$user_type,
                                      levels = c("Very Active", "Moderately Active", "Lightly Active", "Sedentary"))
head(user_type_percent)
```

#### Steps And Minutes Sleep Per Weekday

```{r echo=TRUE}
#steps and minutes asleep per weekday
weekday_steps_sleep <- daily_activity_sleep %>% 
  mutate(weekday = weekdays(date))

weekday_steps_sleep$weekday <- ordered(weekday_steps_sleep$weekday,
                                       levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))

weekday_steps_sleep <- weekday_steps_sleep %>% 
  group_by(weekday) %>% 
  summarize(daily_steps = mean(totalsteps), daily_sleep = mean(totalminutesasleep))
head(weekday_steps_sleep)
```

#### Hourly Steps Throughout The Day

```{r echo=TRUE}
#hourly steps throughout the day
hourly_steps <- hourly_steps %>% 
  separate(date_time, into = c("date","time"), sep = " ") %>% 
  mutate(date = ymd(date))
head(hourly_steps)
```

#### Days Smart Device Used

```{r echo=TRUE}
#daily device usage by user
daily_use <- daily_activity_sleep %>% 
  group_by(id) %>% 
  summarize(days_used = sum(n())) %>% 
  mutate(usage = case_when(
    days_used >= 1 & days_used <= 10 ~ "Low Usage",
    days_used >= 11 & days_used <= 20 ~ "Moderate Usage",
    days_used >= 21 & days_used <= 31 ~ "High Usage"
  ))
head(daily_use)
```

```{r echo=TRUE}
#create daily usage data frame with daily use percentage
daily_use_percent <- daily_use %>% 
  group_by(usage) %>% 
  summarize(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(usage) %>% 
  summarize(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))

daily_use_percent$usage <- factor(daily_use_percent$usage,
                                  levels = c("High Usage",
                                             "Moderate Usage", 
                                             "Low Usage"))
head(daily_use_percent)
```

#### Smart Device Usage By Minutes

```{r echo=TRUE}
#minutes device used by user per day
daily_use_merged <- merge(daily_activity, daily_use, by = c("id"))
head(daily_use_merged)

minutes_worn <- daily_use_merged %>% 
  mutate(total_minutes_worn = veryactiveminutes + fairlyactiveminutes + sedentaryminutes) %>% 
  mutate(percent_minutes_worn = (total_minutes_worn/1440)*100) %>% 
  mutate(worn = case_when(
    percent_minutes_worn == 100 ~ "All Day",
    percent_minutes_worn <= 100 & percent_minutes_worn >= 50 ~ "Half Day",
    percent_minutes_worn <= 50 & percent_minutes_worn >= 0 ~ "Less Than Half Day"
  ))
head(minutes_worn)
```

```{r echo=TRUE}
#create data frame by categories
minutes_worn_percent <- minutes_worn %>% 
  group_by(worn) %>% 
  summarize(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(worn) %>% 
  summarize(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))

minutes_worn_high_usage <- minutes_worn %>% 
  filter(usage == "High Usage") %>% 
  group_by(worn) %>% 
  summarize(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(worn) %>% 
  summarize(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))

minutes_worn_mod_usage <- minutes_worn %>% 
  filter(usage == "Moderate Usage") %>% 
  group_by(worn) %>% 
  summarize(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(worn) %>% 
  summarize(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))

minutes_worn_low_usage <- minutes_worn %>% 
  filter(usage == "Low Usage") %>% 
  group_by(worn) %>% 
  summarize(total = n()) %>% 
  mutate(totals = sum(total)) %>% 
  group_by(worn) %>% 
  summarize(total_percent = total/totals) %>% 
  mutate(labels = scales::percent(total_percent))
```

```{r echo=TRUE}
minutes_worn_high_usage$worn <- factor(minutes_worn_high_usage$worn, 
                                       levels = c("All Day", "Half Day", 
                                                  "Less Than Half Day"))
minutes_worn_mod_usage$worn <- factor(minutes_worn_mod_usage$worn, 
                                      levels = c("All Day", "Half Day", 
                                                 "Less Than Half Day"))
minutes_worn_low_usage$worn <- factor(minutes_worn_low_usage$worn, 
                                      levels = c("All Day", "Half Day", 
                                                 "Less Than Half Day"))
```

```{r echo=TRUE}
head(minutes_worn_percent)
head(minutes_worn_high_usage)
head(minutes_worn_mod_usage)
head(minutes_worn_low_usage)
```

## Share

### Guiding Questions:

-   **Were you able to answer the business questions?**

Yes, we are able to find the usage trends by users, and daily activity levels by consumers.

-   **What story does your data tell?**

It is found that 50% of users are very active and using smart devices daily to measure their activity level and daily sleep routine.

-   **How do your findings relate to your original question?**

The findings explained all the original questions we are trying to get answers.

-   **Who is your audience? What is the best way to communicate with them?**

The audience here is the **Urška Sršen** and **Sando Mur**, the best way to present the findings is to prepare a complete presentation with the visuals and explain them.

-   **Can data visualization help you share your findings?**

Data visualization provides detail trends, and insights of consumers by using graphic visuals that helps in understanding analysis easily.

-   **Is your presentation accessible to your audience?**

The presentation is available upon request but is not freely available. This notebook with the analysis is however accessible.

### Key Tasks:

-   **Determine the best way to share your findings** - completed

-   **Create effective data visualizations** - completed

-   **Present your findings** - completed

-   **Ensure your work is accessible** - completed

### Deliverable:

Supporting visualizations and key findings.

#### Data Visualization:

```{r echo=TRUE}
#visualize user type distribution
user_type_percent %>% 
  ggplot(aes(x = "", y = total_percent, fill=user_type)) + geom_bar(stat = "identity", width = 1) + 
  coord_polar("y", start = 0) + theme_minimal() + theme(axis.title.x = element_blank(), axis.line.y = element_blank(), 
                                                        panel.border = element_blank(), panel.grid = element_blank(), 
                                                        axis.ticks = element_blank(), axis.text.x = element_blank(), 
                                                        plot.title = element_text(hjust = 0.5, size = 14, face = "bold")) + 
  scale_fill_manual(values = c("#85e085", "#e6e600", "#ffd480", "#ff8080")) + 
  geom_text(aes(label = labels), position = position_stack(vjust = 0.5)) + labs(title = "User Type Distribution") 
```

```{r echo=TRUE}
#visualize steps and minutes asleep per weekday
ggarrange(
  ggplot(weekday_steps_sleep) + geom_col(aes(weekday, daily_steps, fill="#006699")) + 
    geom_hline(yintercept = 7500) + labs(title = "Daily Steps Per Weekday", x='', y="") + 
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1)),
  ggplot(weekday_steps_sleep) + geom_col(aes(weekday, daily_sleep, fill="#85e0e0")) + 
    geom_hline(yintercept = 480) + labs(title = "Minutes Asleep Per Weekday", x="", y="") + 
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
)
```

```{r echo=TRUE}
#visualize hourly steps throughout the day
hourly_steps %>% 
  group_by(time) %>% 
  summarize(average_steps = mean(steptotal)) %>% 
  ggplot() + geom_col(aes(x=time, y=average_steps, fill=average_steps)) + 
  labs(title = "Hourly Steps Throughout The Day", x="", y="") + 
  scale_fill_gradient(low = "green", high = "red") + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r echo=TRUE}
#visualize correlation between Daily Steps vs Daily Sleep & Daily Steps vs Daily Calories
ggarrange(
  ggplot(daily_activity_sleep, aes(x=totalsteps, y=totalminutesasleep)) + 
    geom_jitter() + geom_smooth(color = "red") + 
    labs(title = "Daily Steps vs Daily Sleep", x = "Daily Steps", y = "Daily Sleep") + 
    theme(panel.background = element_blank(), plot.title = element_blank()),
  ggplot(daily_activity_sleep, aes(x=totalsteps, y=calories)) + 
    geom_jitter() + geom_smooth(color = "red") + 
    labs(title = "Daily Steps vs Calories", x="Daily Steps", y="Calories") + 
    theme(panel.background = element_blank(), plot.title = element_blank())
)
```

```{r echo=TRUE}
#visualize daily device use by user percentage
daily_use_percent %>% 
  ggplot(aes(x = "", y = total_percent, fill = usage)) + 
  geom_bar(stat = "identity", width = 1) + 
  coord_polar("y", start = 0) + theme_minimal() + 
  theme(axis.title.x = element_blank(), axis.title.y = element_blank(), 
        panel.border = element_blank(), panel.grid = element_blank(), 
        axis.ticks = element_blank(), axis.text.x = element_blank(), 
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold")) + 
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5)) + 
  scale_fill_manual(values = c("#006633","#00e673","#80ffbf"), 
                    labels = c("High Usage - 21 to 31 days", 
                               "Moderate Usage - 11 to 20 Days", 
                               "Low Usage - 1 to 10 Days")) + 
  labs(title = "Daily Device Usage")
```

```{r echo=TRUE}
#visualize data frames by categories
ggarrange(
  ggplot(minutes_worn_percent, aes(x="", y=total_percent, fill=worn)) + 
    geom_bar(stat = "identity", width = 1) + coord_polar("y", start = 0) + 
    theme_minimal() + theme(axis.title.x = element_blank(),
                            axis.title.y = element_blank(), 
                            panel.border = element_blank(),
                            panel.grid = element_blank(), 
                            axis.ticks = element_blank(), 
                            axis.text.x = element_blank(), 
                            plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
                            plot.subtitle = element_text(hjust = 0.5)) + 
    scale_fill_manual(values = c("#004d99", "#3399ff", "#cce6ff")) + 
    geom_text(aes(label = labels), position = position_stack(vjust = 0.5), size = 3.5) + 
    labs(title = "Time Worn Per Day", subtitle = "Total Users"),
  ggarrange(
    ggplot(minutes_worn_high_usage, aes(x="", y=total_percent, fill=worn)) + 
      geom_bar(stat = "identity", width = 1) + 
      coord_polar("y", start = 0) + theme_minimal() + theme(axis.title.x = element_blank(),
                                                            axis.title.y = element_blank(),
                                                            panel.border = element_blank(),
                                                            axis.ticks = element_blank(),
                                                            axis.text.x = element_blank(),
                                                            plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
                                                            plot.subtitle = element_text(hjust = 0.5), 
                                                            legend.position = "none") + 
      scale_fill_manual(values = c("#004d99", "#3399ff", "#cce6ff")) + geom_text_repel(aes(label = labels),
                                                                                       position = position_stack(vjust = 0.5), size = 3) + 
      labs(title = "", subtitle = "High Usage - Users"),
    ggplot(minutes_worn_mod_usage, aes(x="", y=total_percent, fill=worn)) + 
      geom_bar(stat = "identity", width = 1) + 
      coord_polar("y",start = 0) + theme_minimal() + theme(axis.title.x = element_blank(),
                                                           axis.title.y = element_blank(),
                                                           panel.border = element_blank(),
                                                           axis.ticks = element_blank(),
                                                           axis.text.x = element_blank(),
                                                           plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
                                                           plot.subtitle = element_text(hjust = 0.5),
                                                           legend.position = "none") + 
      scale_fill_manual(values = c("#004d99", "#3399ff", "#cce6ff")) + geom_text_repel(aes(label = labels),
                                                                                       position = position_stack(vjust = 0.5), size = 3) + 
      labs(title = "", subtitle = "Moderate Usage - Users"),
    ggplot(minutes_worn_low_usage, aes(x="", y=total_percent, fill=worn)) + 
      geom_bar(stat = "identity", width = 1) + 
      coord_polar("y", start = 0) + theme_minimal() + theme(axis.title.x = element_blank(),
                                                            axis.title.y = element_blank(),
                                                            panel.border = element_blank(),
                                                            axis.ticks = element_blank(),
                                                            axis.text.x = element_blank(),
                                                            plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
                                                            plot.subtitle = element_text(hjust = 0.5),
                                                            legend.position = "none") + 
      scale_fill_manual(values = c("#004d99", "#3399ff", "#cce6ff")) + geom_text_repel(aes(label = labels),
                                                                                       position = position_stack(vjust = 0.5), size = 3) + 
      labs(title = "", subtitle = "Low Usage - Users")
  )
)

```

## Act

### Guiding Questions:

-   **What is your final conclusion based on your analysis?**

The data provides information about the Fitbit users\' usage of the device, their activities and progress over time, as well as insights about the device\'s performance, which seemed consistent with established research.

-   **How could your team and business apply your insights?**

The trends and insights shows that there are large number of women who are actively using the Bellabeat's devices, but there are also large number of potential consumers available that can targeted with the help of an effective marketing strategy.

-   **What next steps would you or your stakeholders take based on your findings?**

I would recommend a more in-depth analysis on the long use smart devies, however there is enough data to support a digital marketing campaign.

-   **Is there additional data you could use to expand on your findings?**

Additional data that would expand the findings would include: demographic data, health data, daily activity, and marketing campaign history.

### Key Tasks:

-   **Create your portfolio** - completed

-   **Add your study** - completed

-   **Practice presenting your case study to your friend or a family member** - completed

### Deliverable:

After analyzing the data, we have found that there are number of trends that can help in online target marketing campaign and improve Bellabeat app:

-   Daily notifications of steps taken and also post content on app to motivate users to reach their daily steps goal.

-   Allow users to set notification reminders of sleep time to prepare for sleep and guide them with effective sleeping techniques and habits.

-   Bellabeat should introduce a reward system in app to motivate users to reach target goals set by them by giving users free giveaways and discounts on membership fees.

## Conclusion

Bellabeat can improve their device usage by consumers by rewarding them with discounts on completing their daily goals, and should target new potential consumers by a strategic marketing campaign.
